A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-18 paper/ch_potentials.tex
some exp improvement

With this setup CH-Potentials support turns without requiring turn information in the CH.

@@

The first experiment varies the tightness of the heuristic.
The lower bound $w_\ell$ is set to the freeflow travel time.
The query weights $w_q$ are set to $\alpha \cdot w_\ell$, where $\alpha\ge 1$.
% When $\alpha = 1$, the heuristic is tight.
Increasing $\alpha$ degrades the heuristic's quality.
Figure~\ref{fig:scaled_weights} depicts the results.
\todo{decrease figure height}
Clearly, $\alpha$ has significant influence on the running time.
Average running times range from below a millisecond to a few hundred milliseconds depending on $\alpha$.
Up to around $\alpha = 1.1$ the running time grows quickly.
After $\alpha = 1.1$ the growth slows down.
This illustrates both the strengths and limits of our approach and goal directed search in general.
Goal directed search (and thus CH-Potentials) can only achieve competitive running times if the application allows for a sufficiently tight heuristic.

>>>>

With this setup, CH-Potentials support turns without requiring turn information in the CH.

@@

The performance of A* depends on the tightness of the heuristic.
CH-Potentials computes optimal distance estimates with respect to $w_\ell$.
However, for most applications, there will be a gap between $w_q$ and $w_\ell$ (otherwise we could use an unmodified CH).
We evaluate the impact of the difference between $w_q$ and $w_\ell$ on the performance of A*.
The lower bound $w_\ell$ is set to the freeflow travel time.
The query weights $w_q$ are set to $\alpha \cdot w_\ell$, where $\alpha\ge 1$.
% When $\alpha = 1$, the heuristic is tight.
Increasing $\alpha$ degrades the heuristic's quality.
Figure~\ref{fig:scaled_weights} depicts the results.
\todo{decrease figure height}
Clearly, $\alpha$ has significant influence on the running time.
Average running times range from below a millisecond to a few hundred milliseconds depending on $\alpha$.
Up to around $\alpha = 1.1$ the running time grows quickly.
After $\alpha = 1.1$ the growth slows down.
This illustrates both the strengths and limits of our approach and goal directed search in general.
CH-Potentials can only achieve competitive running times if the application allows for a sufficiently tight lower bounds at preprocessing time.
